`lancer` Output Examples

### 2023-01-04 README.qmd
Fix typo.
Replace dilution with curve in Quarto Example folder.

Here is where I store some output example of the R package [`lancer`](https://github.com/SLINGhub/lancer)

@@

[`dilution_summary.xlsx`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/dilution_summary.xlsx) is the output in Excel.

@@

[`dilution_plot.pdf`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/dilution_plot.pdf) is the output in pdf.

@@

https://lancer-interactive-example.netlify.app is the output as an interactive trellis plot from the `Dilution_Plot_Folder` when the `index.html` file is clicked.

>>>>

Here is where I store some output example of the R package [`lancer`](https://github.com/SLINGhub/lancer).

@@

[`curve_summary.xlsx`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/curve_summary.xlsx) is the output in Excel.

@@

[`curve_plot.pdf`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/curve_plot.pdf) is the output in pdf.

@@

https://lancer-interactive-example.netlify.app is the output as an interactive trellis plot from the `Curve_Plot_Folder` when the `index.html` file is clicked.
